\begin{thebibliography}{99}
\bibitem{ref01}蔡文. \emph{可拓集合和不相容问题[J]}. 科学探索学报, (1983)(1), 83-97.\\Cai Wen. (1983) The extension set and incompatible problem [J]. Journal of Scientific Exploration 1: 83-97.
\bibitem{ref02}蔡文. \emph{可拓论及其应用[J]}. 科学通报, (1999),44(7), 673-682.\\Cai Wen. Extension Theory and Its Application[J]. Chinese Science Bulletin, (1999),44(7)，673-682.
\bibitem{ref03}蔡文，杨春燕，林伟初. 可拓工程方法[M]. 科学出版社，北京. 2000.\\
Cai Wen，Yang Chun-yan，Lin Wei-chu. Method of Extension Engineering[M]. Science Press in China, Beijing,2000.
\bibitem{ref04}曹炳元. 物元分析法及其在投资决策中的应用[C]. 中国第二次物元分析学术讨论会论文选. 广州, 1986.\\
   Cao Bing-yuan. Matter element analysis method and its application in the investment decision-making[C]. Selected Papers of the Second Symposium on Matter Element Analysis of China's, Guangzhou, 1986.
\bibitem{ref05}曹炳元. 可拓凸集. 湖南师范大学自然科学学报[J], 1990,Vol.13,  No.1, 18-24.\\
Cao Bing-yuan. Extension convex set[J]. Acta Science Naturalium Univ. Norm Hunanenist, 1990,Vol.13, No.1, 18-24.
\bibitem{ref06}曹炳元. 可拓凸集分离定理的进一步研究. 长沙水电师院学报 (自然科学版) [J], 1994，Vol.9, No.3, 229-234.\\
   Cao Bing-yuan. Futher study of extension-convex-set-separate theorem[J]. Natural Science Journal of Changsha Normal University of Water Resources and Electric Power, 1994，Vol.9, No.3, 229-234.
\bibitem{ref07}曹炳元. 区间和Fuzzy（值）凸函数和凸泛函[J]. 广州大学学报(自然科学版)，2008，Vol.8，No.4, 1998, 1-5.\\
   Cao Bing-yuan.Interval and fuzzy （value）convex function with convex functional[J]. Journal of Guangzhou University (Natural Science Edition)，2008，Vol.8，No.4, 1998, 1-5.
\bibitem{ref08}Christelle Guéret, Christian Prins, Marc Sevaux. 运筹学案例---建模，求解[M]. Dash Optimization有限公司，2002.\\
   Christelle Guéret, Christian Prins, Marc Sevaux. Operations Research Case --- Modeling, solving [M]. Dash Optimization Ltd，2002.
\bibitem{ref09}沈括. 刘晏籴粮术. 梦溪笔谈. \\http://read.dayoo.com/book/content-10824-636986.htm/\\
   Shen Gua. Liu Yan buy up grain surgery（method）. Meng Xi Bi Tan. \\ http://read.dayoo.com/book/content-10824-636986.htm/
\bibitem{ref10}余耀华. 大唐财相：刘晏. 华文出版社. \\http://www.hongxiu.com/x/16350/\\
Yu Yao-hua. Datang Finance Minister: Liu Yan. Chinese Press. \\http://www.hongxiu.com/x/16350/
\end{thebibliography}
